A Stochastic Quasi-Newton Optimizer for \texttt{TensorFlow}

### 2018-05-06 presentation/main.tex
Paper and presentation

\begin{frame}[t]{Implementation}
  \begin{itemize}
    \item Implementing L-BFGS proved challenging, and we discovered why it wasn't
      part of the library already!
    \item Following the advice from the discussion of 
      \href{https://github.com/tensorflow/tensorflow/issues/446}{Issue 446}, we
      implemented L-BFGS as an \texttt{ExternalOptimizerInterface}.
    \item This allowed us to write \texttt{NumPy} code but ``plug in'' to
      \texttt{TensorFlow}.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}[t]{Implementation}
  \begin{itemize}
    \item Implementing SdLBFGS proved challenging, and we discovered why it wasn't
      part of the library already!
    \item Following the advice from the discussion of 
      \href{https://github.com/tensorflow/tensorflow/issues/446}{Issue 446}, we
      implemented SdLBFGS as an \texttt{ExternalOptimizerInterface}.
    \item This allowed us to write \texttt{NumPy} code but ``plug in'' to
      \texttt{TensorFlow}.
  \end{itemize}
\end{frame}
